---
title: "Assignment Sample"
author: "Student name"
date: "3/2/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
course: STA 6257 - Advance Statistical Modeling
---

# Problem A

**
A study was conducted to determine how to maximize Mermaid meadowfoam flower production for extraction as vegetable oil.
**
```{r}

# loading package 
library(GLMsData)
library(DT)
data(flowers)
# to display the data set from the loaded package
datatable(flowers)
```

```
There are 3 variables and 24 observations in flowers data set. The response variable is the mean number of flowers per meadowfoam plant.
```
**
1.Plot  the  average  number  of  flowers  produced  per  plant  against  the  light  intensity,  distinguishing the two timings.  Comment.
**
```{r}
# Plotting
plot(Flowers ~ Light,data=flowers, pch=ifelse(Timing=="Before",1,19),las=1,
     xlab="Light", ylab="Mean number of flowers per meadowfoam",
     xlim=c(120, 1000), ylim=c(20, 90))
legend("bottomleft", pch=c(1,19), legend=c("Before","PFI"))

```

```
Comment here... 
```

**
2.Suppose a model with the systematic component Flowers ~ Light + Timing was needed to model the data. What would such a systematic component imply about the relationship between the variables?
**
```
Answer here...
```
**
3.Suppose a model with the systematic component Flowers ~ Light + Timing + Light: Timing was needed to model the data. What would such a systematic component imply about the relationship between the variables?
**

```
Answer here...
```
**
4.Fit the two linear regression models with the systematic components specified above. Give the regression tables and comment.
**

```{r}
# Fit model without interaction
m1=lm(Flowers~Light + Timing,data = flowers)
summary(m1)
```

```
comment here...
```

```{r}
# Fit model with interaction
m2=lm(Flowers~Light*Timing,data = flowers)
summary(m2)

```

```
Comment here...

```

**
5.Perform a diagnostic analysis on the fitted linear regression models. Present the residuals plots and comment.
**

```{r}
# Model without interaction
par(mfrow=c(2,2))
plot(m1)
```

```
  comment here ... 
```

```{r}
# Model with interaction
par(mfrow = c(2,2))
plot(m2)

```

```
 Comment here ...
```
**
6.Identify any influential observations or outliers?
**

```{r}
# Model without interaction
rowSums(influence.measures(m1)$is.inf)

```

```
 Comment here ...
```

```{r}
# Model with interaction
rowSums(influence.measures(m2)$is.inf)
```
 
``` 
Comment here ...
```

**
7.What is the best model? Why?
**

```{r}
# comparing models
anova(m1,m2)


```

```
 comment here...
```

**
8.Interpret the final model (best model)
**
```{r}
library(ggplot2)
# plot regression lines
ggplot(flowers,aes(x=Light,y=Flowers,col=Timing))+geom_point()+geom_smooth(method = "lm", formula = y~x, se = TRUE, level=0.8 )


```

```
 The results indicate that the light intensity is significant
 after adjusting for the other variables.
 The coefficient is negative suggesting that greater light intensity 
 is associated with lower mean number of flowers
 If there were interaction this interpretation is only valid for Timing == Before
```
